---
title: "**Points allocation in the Eurovision Song Contest**"
author: "Paul Gering"
output:
  html_document: default
  word_document: default
  pdf_document: default
---


```{r echo = FALSE, result = FALSE, warning = FALSE, message = FALSE, error = FALSE, out.width = "65%", fig.align = "center"}

#Load here package
if (!require('here')) 
{
  install.packages('here');
}
library(here)

# Show Eurovision logo in Markdown file
logo <- here("figs","esc.jpg")
knitr::include_graphics(logo)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE, rows.print = 5, fig.align = "center")
```

# Introduction
### Background

This project will use data from the **Eurovision Song Contest**. The Eurovision Song Contest is a yearly competition where different countries submit an artist and song to compete in a live televised event against other countries. Each participating country awards points to their favourite songs and the country with the most points is allowed to host the contest the following year. 
The first contest took place in 1956 and included 14 songs from 7 countries. Since then, the contest has grown dramatically, with the 2022 competition hosted in Turin Italy including songs from 40 countries. In recent years, the competition has gained popularity in countries outside Europe, with Australia joining the contest in 2015, the competition being televised in China and America, and America staging their own version of the competition in 2022 called the "American Song Contest". 

Over the 67 years that the competition has been held, the voting system used to determine the winning song has changed drastically. Changes in the voting system have affected the number of points awarded to each country and therefore, the points total needed to win the competition.

### Project Aim
This project will seek to visualize how changes in the **voting system** have affected the number of points allocated in each year. Specifically, this project will seek to visualise differences in the number of **points** accumulated by the **winning song** in each year of the competition, and how this relates to the voting system used in each year. 

### Project organization 
The /raw folder contains the raw data used for this project and /figs contains the figures produced from this project. 

A codebook can be found in the project folder, which describes the variables and the functions used in the project. 

### Loading Packages
The renv package was used to store the packages used in this project, and to keep an account of the package versions that were used. These can be found in the file /renv.lock.

```{r loadlib, echo = TRUE, results = 'hide', warning = FALSE, message = FALSE}
#Load packages with renv
if (!require('renv')) 
{
  install.packages('renv');
}
library(renv)
renv::restore()

#Load packages
library(dplyr)
library(ggplot2)
library(here)
library(janitor)
library(plotly)
library(tidyverse)
library(toOrdinal)
library(rvest)
library(htmlwidgets)
```

### Data Origins 
The raw data was scraped from the Eurovision Website <https://eurovision.tv/history>. The data for each year of the competition is located in nested links from this page. You can only access the data from one year at a time, by selecting the year that you would like to view on this page. Selecting the year would take you to an overview page that would appear in the following format <https://eurovision.tv/event/turin-2022>. From this link, you have to select whether to view data from the semi finals or the final. Semi-finals were introduced in the 2004 competition as a way of allowing more countries to compete. This project is only interested in gathering data from the final shows since this will contain the data relating to the winning songs. The following link contains a data table showing the results from the 2022 competition "https://eurovision.tv/event/turin-2022/final". The data is presented in the same format for each year of the competition. For this project, I needed to scrape the tables from the URLs for each year and combine them into a large dataset.

### Data scraping

I first had to scrape the URL links that contained the datatables for each year. These links were scraped from the page <https://eurovision.tv/history> using the web browser SelectorGadget. A problem I encountered at this stage was that the URL links varied in an unexpected way. For the competitions before 2004, the URL link finished with "/final". However, for competitions that included a semi final (from 2004 onwards), the URL link finished with "/grand-final". This inconsistency meant that I was unable to scrape all the URL links using a single piece of code. To resolve this issue, I had to scrape the data using four sets of code. One set of code was used to scrape data from page 1, containing the year links for competitions between 2007 and 2022. Another set of code was used to scrape the year links from pages 3, 4 and 5, which contained year links for the competitions between 1956 and 1991. Two sets of code had to be used to scrape data from page 2, which contained data from competitions that had "/final" at the end of their URL (1992-2003) and "/grand-final" at the end of their URL (2004-2006). Once I had collected the URL links, I scraped the data tables from each URL link using the lapply() function. The scraped tables were added to a new dataframe in R, resulting in four dataframes being created to contain the data scraped from each set of code. Below is an example of the code used to scrape data from pages 3, 4 and 5. 


```{r message = FALSE}

#-----------SCRAPING DATA FROM PAGES 3, 4 & 5 -------------

scrape56 <- data.frame() # declaring scrape56 will be a data frame

# using for loop to download the URL's for from multiple pages
for(page_result in 2:4) {
  link = paste0("https://eurovision.tv/history?page=", page_result)
  page = read_html(link)
  
  # getting nested links for each year of the contest
  year_links = page %>% 
    html_nodes(".views-field-field-event-year a") %>%             # Asking R to find this data on the webpage
    html_attr("href") %>%                                         # Extract href (e.g., turin-2022) from scraped data
    paste0("https://eurovision.tv", ., "/final")                  # Pasting the href into the URL
  
  # retrieving the tables and the years from each nested link
  get_data <- lapply(year_links, function(i) {
    year_page = read_html(i)                                      # Reading each URL link into R
    year_data = year_page %>% 
      html_nodes("table.cols-7") %>% 
      html_table() %>%  
      .[[1]]                                                      # Scraping the data tables from each URL link
    year <- str_extract(i, "\\d{4}")                              # Extracting the year from the URL links
    year_data$year <- year                                        # Adding the year data to the data tables
    
    
    return(year_data)                                             # Asking R to return the datatable 
  })
  # Adding all data to a new datatable called scrape56
  scrape56 = rbind(scrape56, data.table::rbindlist(get_data))
  
}

```


```{r echo = FALSE}

#-----------SCRAPING DATA FROM PAGE 1 -------------

scrape07 <- data.frame() # declaring scrape07 will be a data frame

link = "https://eurovision.tv/history"
page = read_html(link) # downloading the link for page 1


# getting nested links for each year of the contest on page 1
year_links = page %>% 
  html_nodes(".views-field-field-event-year a") %>%               # Asking R to find this data on the webpage
  html_attr("href") %>%                                           # Extract href (e.g., turin-2022) from scraped data
  paste("https://eurovision.tv", ., "/grand-final", sep="")       # Pasting the href into the URL


# retrieving the tables and the years from each year link
get_data <- lapply(year_links, function(i) {
  year_page = read_html(i)                                        # Reading each URL link into R
  year_data = year_page %>% 
    html_nodes("table.cols-7") %>% 
    html_table() %>% 
    .[[1]]                                                        # Scraping the data tables from each URL link
  year <- str_extract(i, "\\d{4}")                                # Extracting the year from the URL links
  year_data$year <- year                                          # Adding the year data to the data tables
  
  return(year_data)                                               # Asking R to return the datatable 
})


# Adding all data to a new datatable called scrape07
scrape07 = data.table::rbindlist(get_data)


#-----------SCRAPING DATA FROM PAGE 2 (2004:2006) -------------


scrape04 <- data.frame() # declaring scrape04 will be a data frame

link = "https://eurovision.tv/history?page=1"
page = read_html(link) # downloading the link for page 2


# getting nested links for 2004, 2005 and 2006 competitions from page 2
year_links = page %>% 
html_nodes("tr:nth-child(2) .views-field-field-event-year a , 
tr:nth-child(3) .views-field-field-event-year a , 
tr:nth-child(1) .views-field-field-event-year a") %>%             # Asking R to find this data on the webpage
  html_attr("href") %>%                                           # Extract href (e.g., turin-2022) from scraped data
  paste("https://eurovision.tv", ., "/grand-final", sep="")       # Pasting the href into the URL


# retrieving the tables and the years from each year link
get_data <- lapply(year_links, function(i) {
  year_page = read_html(i)                                        # Reading each URL link into R
  year_data = year_page %>% 
    html_nodes("table.cols-7") %>% 
    html_table() %>%  
    .[[1]]                                                        # Scraping the data tables from each URL link
  year <- str_extract(i, "\\d{4}")                                # Extracting the year from the URL links
  year_data$year <- year                                          # Adding the year data to the data tables
  
  return(year_data)                                               # Asking R to return the datatable 
})

# Adding all data to a new datatable called scrape04
scrape04 = data.table::rbindlist(get_data)


#-----------SCRAPING DATA FROM PAGE 2 (1991:2003) -------------


scrape92 <- data.frame() # declaring scrape92 will be a data frame

link = "https://eurovision.tv/history?page=1"
page = read_html(link) # downloading the link for page 2


# getting nested links for 1992-2003 competitions from page 2
year_links = page %>% 
html_nodes("tr:nth-child(5) .views-field-field-event-year a , 
tr:nth-child(6) .views-field-field-event-year a , 
tr:nth-child(7) .views-field-field-event-year a , 
tr:nth-child(8) .views-field-field-event-year a ,
tr:nth-child(9) .views-field-field-event-year a , 
tr:nth-child(10) .views-field-field-event-year a , 
tr:nth-child(11) .views-field-field-event-year a , 
tr:nth-child(12) .views-field-field-event-year a , 
tr:nth-child(13) .views-field-field-event-year a , 
tr:nth-child(14) .views-field-field-event-year a , 
tr:nth-child(15) .views-field-field-event-year a , 
tr:nth-child(4) .views-field-field-event-year a") %>%             # Asking R to find this data on the webpage
  html_attr("href") %>%                                           # Extract href (e.g., turin-2022) from scraped data
  paste("https://eurovision.tv", ., "/final", sep="")             # Pasting the href into the URL


# retrieving the tables and the years from each year link
get_data <- lapply(year_links, function(i) {
  year_page = read_html(i)                                        # Reading each URL link into R
  year_data = year_page %>% 
    html_nodes("table.cols-7") %>% 
    html_table() %>%  
    .[[1]]                                                        # Scraping the data tables from each URL link
  year <- str_extract(i, "\\d{4}")                                # Extracting the year from the URL links
  year_data$year <- year                                          # Adding the year data to the data tables
  
  return(year_data)                                               # Asking R to return the datatable 
})


# Adding all data to a new datatable called scrape92
scrape92 = data.table::rbindlist(get_data)
```

### Combining the scraped data
Once I had scraped all the Eurovision data, the four dataframes were combined using the function rbind(). The final dataframe containing all the data was saved as a CSV file.

```{r message = FALSE}
# Combining the four datasets into a dataframe and saving it as a csv

df_esc <- rbind(scrape07, scrape04, scrape92, scrape56)

write.csv(df_esc, here("raw", "esc_raw_data.csv"))

```

### A limitation of this data scraping method

To scrape the URL's from the second page on the Eurovision website <https://eurovision.tv/history?page=1>, two sets of code had to be used. These codes were identical except one piece of code scraped URL links ending in "final" and the other scraped URL links ending in "/grand-final". For this method to work, SelectorGadget was used to highlight the location of the year links that I wanted to scrape for each piece of code. This means that my code to scrape data from page 2 is dependent of the location of the year links on this page. Once the data from a new competition is added to the Eurovision website, this may shift the location of the year links on this page, which will affect the data that is scraped by my R code. For example, code that is designed to scrape URL's that end with "/final" may try to scrape URL's from the 2004 competition. This could prevent the R code from working because R is attempting to locate a URL that does not exist.

By saving the scraped data as a CSV file, I have tried to minimise the impact that changes to the Eurovision website have on this R project. The rest of the R code, that is focused on data management and visualisation, will run based off the data in this CSV file. 

```{r}

df <- read.csv(here("raw", "esc_raw_data.csv"))
head(df)

```

### Description of the data 

The data contains 8 variables, which are: 
  **R/O Sort descending** is the order in which the songs performed in the contest,
  **Half** is whether the country performed in the first or second half of the contest,
  **Country** is the name of the participating country,
  **Participant** is the name of the artist, 
  **Song** is the name of the song,
  **Points** is the total amount of points each country received, 
  **Rank** is the position which the song achieved in the final, and
  **year** is the year of the competition.

# Data Preparation

### Cleaning the column names 

The column names contain capitals and special characters, which may cause errors in the R code and will not look appealing in a visualisation. For this reason, I used the clean_names() function from the janitor package to tidy these names.  

```{r message = FALSE}
#--------------TIDY DATA------------------

# cleaning the column names

df <- clean_names(df)
```

### Removing the duplicate rows for 1969 competition

Since there were multiple winning songs in 1969, the 1969 competition has been repeated four times on the page "https://eurovision.tv/history?page=3". This has resulted in the 1969 data being scraped multiple times. The below code was used to remove the duplicate rows for the 1969 competition.

The same set of code has also been used to drop columns that contain irrelevant data. The following columns were dropped because they contained data that would not be used for the visualisation: half, r_o_sort_descending and x. The x column was added when the data was saved as a CSV and then read into R. The half column only contains data for the 2021 competition, so will not be useful when trying to compare data across the years of the competition. The r_o_sort_descending may have been interesting to visualise, but will not be useful for this visualisation. 

```{r message = FALSE}
df1 <- df %>% 
  select(year, country, participant, song, points, rank) %>% # dropping the unnecessary columns
  unique() #remove duplicate rows 
```

### Replacing missing data in the dataset

There are 51 pieces of missing data in the dataframe, under the points column. The Eurovision Website is inconsistent in how it represents zero points in the datatables, with some years using the number zero and others using a blank space. When the data was scraped from the Eurovision website, these blank spaces were converted to NA's. Since the NA's may lead to errors when visualising the data, I converted them back into zeros.

A large proportion of the missing data is from the 1956 competition. The reason for this is that the points allocation process was not made public for the 1956 competition. The lack of any useful points data for the 1956 competition meant that this data could be removed from the dataframe.

```{r message = FALSE}
# To count the NA's in each column: colSums(is.na(df))
# Dealing with missing data
df2 <- df1 %>% 
  replace_na(list(points = 0)) %>% # replace missing data with 0's
  filter(year != 1956) # filter out data from 1956
```

### Additional information added to the dataframe

**Voting system data** was taken manually from the website Eurovision.World.com, a fan website dedicated to the Eurovision Song Contest (<https://eurovisionworld.com/esc/voting-systems-in-eurovision-history>). The reason this website was chosen was because the information is not presented on the Eurovision website. Other information on the Eurovision.World.com has been checked with the Eurovision website for accuracy such as the points totals in specific years of the competition. The voting system data was not scraped directly from Eurovision.World.com because the data was not presented in a format that would complement a visualisation. The descriptions were too long and may have been difficult for a non-Eurovision fan to understand. Instead, the data was summarised and added to seven voting systems variables in R. The number at the end of each variable name represents the year that the voting system was introduced.
Using the mutate function, this data was added to the data frame as new column called voting system.

```{r message = FALSE}
# Adding voting system data to variables in R

voting_system16 <- "Two sets of points (12, 10, 8, 7, ....1) awarded to ten songs"
voting_system75 <- "One set of points (12, 10, 8, 7, ....1) awarded to ten songs"
voting_system57 <- "10 points split between one to ten songs"
voting_system62 <- "One set of points (3, 2, 1) awarded to three songs"
voting_system64 <- "One set of points (5, 3, 1) awarded to three songs"
voting_system63 <- "One set of points (5, 4, 3, 2, 1) awarded to five songs"
voting_system71 <- "2-10 points awarded to each song"

# adding a new column for voting system to the dataframe

df3 <- df2 %>% 
  mutate(voting_system = case_when(year > 2015 ~ voting_system16,
                                   year > 1974 & year < 2016 ~ voting_system75, 
                                   year == 1957 | year == 1958 | 
                                     year == 1959 | year == 1960 | 
                                     year == 1961 | year == 1967 | 
                                     year == 1968 | year == 1969 |
                                     year == 1970 | year == 1974 ~ voting_system57,
                                   year == 1962 ~ voting_system62, 
                                   year == 1963 ~ voting_system63, 
                                   year == 1971 | year == 1972 | 
                                     year == 1973 ~ voting_system71, 
                                   year == 1964 | year == 1965 | 
                                     year == 1966 ~ voting_system64))

# Changing the order of the voting systems in the dataset so that they appear in chronological order

df3$voting_system <- factor(df3$voting_system, 
                            levels = c("10 points split between one to ten songs", 
                                       "One set of points (3, 2, 1) awarded to three songs", 
                                       "One set of points (5, 4, 3, 2, 1) awarded to five songs",
                                       "One set of points (5, 3, 1) awarded to three songs", 
                                       "2-10 points awarded to each song", 
                                       "One set of points (12, 10, 8, 7, ....1) awarded to ten songs",
                                       "Two sets of points (12, 10, 8, 7, ....1) awarded to ten songs"))

```


### Creating a dataframe with only the winning songs for each year

Since the visualisation will only present data for the winning songs, I needed to filter this data out of the dataset. I felt that it would be a more intuitive and interesting to visualise the points totals for the winning songs than to visualise the total or average number of points.

```{r message = FALSE}
# Filter data that was ranked 1st

df4 <- df3 %>% 
  filter(rank == "1st")

head(df4)
```

The new dataframe contains four rows for the 1969 competition, because there were four winners in 1969. I wanted to collapse these four rows so that the information for all the winning songs, participants and countries appears in a single row. This would be beneficial when adding the information to a scatter plot as it meant that I could add a label to the data containing all the information for the winners in the 1969 competition. Collapsing the four rows was made easier by the fact that the winning songs in 1969 had the same points total, rank and year.

```{r message = FALSE}

# Adding the four country names to each row for 1969, separated by a comma
df4$country <- ifelse(df4$year == 1969,
                      paste(unique(df4$country[df4$year == 1969]), collapse = ", "),
                      df4$country)

# Adding the four song names to each row for 1969, separated by a comma
df4$song <- ifelse(df4$year == 1969,
                       paste(unique(df4$song[df4$year == 1969]), collapse = ", "),
                       df4$song)

# Adding the four participant names to each row for 1969, separated by a comma
df4$participant <- ifelse(df4$year == 1969,
                    paste(unique(df4$participant[df4$year == 1969]), collapse = ", "),
                    df4$participant)

# Removing the duplicate columns for 1969, leaving one row containing all the data from 1969
df5 <- df4 %>% 
  unique()

```


# Visualisation

### Creating visualisation 1

A scatter plot was most appropriate to visualise how the data changed over time. The year was used as the x axis and points as the y axis, with voting system as the grouping variable. The scale of the x axis was manually set to increase in sets of 5 to make the year data easier to read. The size of each point was increased so that more of the graph was filled and the graph would look less empty and more appealing. However, the size was not increased further to avoid too much overlap between the points.

The plot was converted into a plotly interactive graph using the function ggplotly. This meant that the graph contained labels for each point which would appear when they were hovered over with the cursor. The text contained within each label was the year, the winning country, the song, the participant and the number of points they received. This information was important to include as it would provide further context as to why a winning song may have received more or less points. The datapoint for the 1969 competition will contain the data for the four winning songs in the year. Another benefit of using a Plotly graph is that you can double click on a voting system that you would like to display data for and the plot will isolate the datapoints from this voting system. Plotly can make it difficult to display titles, subtitles, and captions on a ggplot graph. These had to be added in once the graph was converted into a plotly graph using the layout() function. The choice was made to display the legend in a horizontal fashion below the graph. This was appropriate as the legend was long and would have reduced the space available for the graph if presented vertically alongside the graph. 

### Labels for the visualisation 

```{r message = FALSE}
#--------------PLOT DATA------------------
# labels that will be added to the plot

plottitle <- "Points allocation in the Eurovision Song Contest"
grouplab <- "Voting system for each country"
caplab <- "Source: eurovision.tv/history"
subtitle <- "Points total of the winning songs 1957-2022"
```


```{r message = FALSE}
### Creating visualisation 1

# constructing the plot using ggplot
# Year as the x axis and share of points on the Y axis
# Voting system used as colour and text added for labels

p1 <- ggplot(df5, mapping = aes(x = year, 
                                y = points, 
                                col = voting_system,
                                text = paste("<br>Year:",year,
                                             "<br>Winning country:",country,
                                             "<br>Artist:",participant,
                                             "<br>Song:", song, 
                                             "<br>Points:",points)))

# Adding additional elements to the plot e.g., points, scale, title and legends

p1 <- p1 + geom_point(size = 2.5) +
  scale_x_continuous(limits = c(1955, 2022), 
                     breaks = seq(1955, 2022, 5)) +
  labs(title = plottitle, 
       x = "Year", 
       y = "Points",
       colour = grouplab)

# Converting the ggplot into a ggplotly animation with hover labels

p1 <- ggplotly(p1, tooltip = c("text"), width = 800,
               height = 600) %>%                                   # Converting to a plotly graph with specified size
  layout(margin = list(l = 30, r = 30, b=60, t = 60, pad = 4),     # Changing the margins of the plot
         title = list(text = paste0(plottitle,
                                    '<br>',
                                    '<sup>',
                                    subtitle,'</sup>')),             # Adding a subtitle to the plot
         annotations = list(x = 1, y = -0.2,
                            text = caplab,
                            showarrow = FALSE,
                            xref = "paper", 
                            yref = "paper", 
                            xanchor="right", yanchor="auto", 
                            xshift = 0, yshift=0, 
                            font=list(size=13)))                   # Adding a annotation to the plot
p1 <- p1 %>%  layout(legend = list(orientation = 'h', 
                             xanchor = "center",
                             x = 0.5, 
                             y =-0.2)) %>%                         # Changing the legend to be horizontal
  style(legendgroup = NULL)

p1

saveWidget(p1, file = here("figs", "points_total_esc.html"))            # Save the plot in the figs folder
```


### Visualisation 1 summary
Visualisation 1 shows that the points totals of the winning songs in the Eurovision Song Contest have increased exponentially over the years. Changes in the points totals have coincided with changes in the voting system, particularly in the early years of the competition. In the first few years, where fewer points were awarded to a smaller number of countries, the points totals for the winning songs were as low as 18 points in 1969, though another explanation for this low points total is that four countries won in that year. Changing the voting system in 1971 led to a rapid increase in the number of points given to the winning song, likely because each country awarded points to each of the songs. Between 1975 and 2003, the same voting system was used, which resulted in the points totals remaining consistent. From the 2004 competition, there is a slight increase in the point totals, which can be explained by the introduction of the semifinals leading to more countries voting in the final. Once the choice was made for each country to allocate two sets of points in 2016, the points totals of the winning songs increased again, leading to the highest points total that has been achieved in the Eurovision Song Contest, Portugal in 2017 with 758 points. 

The aim of this project is partially achieved in visualisation 1. This interactive plot shows how changes in the voting system have affected the points totals of the winning songs. However, this plot does not isolate the effect of the voting system changes from the effect of the increasing number of panticipating countries on points allocation. Therefore, it is unclear whether the changes in the points totals of the winning songs are a result of the changes in the voting system. To accurately visualise how voting system has affected points allocation, a second visualisation was produced controlling for the number of participating countries.

### Adapting the plot to control for the number of countries 
To control for the number of participating countries, I calculated the share of points that the winning songs received in each year. This was calculated by dividing the total number of points awarded in each year by the number of points allocated to the winning song. To do this calculation, I added the share of points column to a version of the dataframe that was not filtered by rank.

```{r message = FALSE}
# Create a new column to show share of points 
df6 <- df3 %>% 
  group_by(year) %>% 
  mutate(share_points = (points/(sum(points))*100))


# Change the share_point column to two decimal places 

df6 $share_points <- round(df6 $ share_points, 2)

df7 <- df6 %>% 
  filter(rank == "1st") # filter data to only include winning songs

# collapsing the four rows for 1969 in the new dataframe

df7$country <- ifelse(df7$year == 1969,
                      paste(unique(df7$country[df7$year == 1969]), collapse = ", "),
                      df7$country)

df7$song <- ifelse(df7$year == 1969,
                   paste(unique(df7$song[df7$year == 1969]), collapse = ", "),
                   df7$song)

df7$participant <- ifelse(df7$year == 1969,
                          paste(unique(df7$participant[df7$year == 1969]), collapse = ", "),
                          df7$participant)

df8 <- df7 %>% 
  unique()

```

### Creating visualisation 2

A new subtitle will be needed for this visualisation: 

```{r message = FALSE}
subtitle2 <- "Share of points of the winning songs 1957-2022"
```

A similar code is used to construct visualisation 2 asvisualisation 1. The only change is that share of points will be used for the y axis instead of points. 

```{r message = FALSE}

# constructing the plot using ggplot
# Year as the x axis and share of points on the Y axis
# Voting system used as colour and text added for labels

p2 <- ggplot(df8, mapping = aes(x = year, 
                                y = share_points, 
                                col = voting_system, 
                                text = paste("<br>Year:",year,
                                             "<br>Winning country:",country,
                                             "<br>Artist:",participant,
                                             "<br>Song:", song,
                                             "<br>Share of Points:",share_points, "%")))

# Adding additional elements to the plot e.g., points, scale, title and legends

p2 <- p2 + geom_point(size = 2.5) +
  scale_x_continuous(limits = c(1955, 2022), 
                     breaks = seq(1955, 2022, 5)) +
  labs(title = plottitle, 
       x = "Year", 
       y = "Share of points (%)", 
       colour = grouplab)

# Converting the ggplot into a ggplotly animation with hover labels

p2 <- ggplotly(p2, tooltip = c("text"), width = 700,
               height = 600) %>%                                    # Converting to a plotly graph with specified size
  layout(margin = list(l = 30, r = 30, b=60, t = 60, pad = 4),      # Changing the margins of the plot
         title = list(text = paste0(plottitle,
                                    '<br>',
                                    '<sup>',
                                    subtitle,'</sup>')),             # Adding a subtitle to the plot
         annotations = list(x = 1, y = -0.2,
                            text = caplab,
                            showarrow = FALSE,
                            xref = "paper", 
                            yref = "paper", 
                            xanchor="right", yanchor="auto", 
                            xshift = 0, yshift=0, 
                            font=list(size=13)))                    # Adding a annotation to the plot
p2 <- p2 %>%  layout(legend = list(orientation = 'h', 
                             xanchor = "center",
                             x = 0.5, 
                             y =-0.2)) %>%                          # Changing the legend to be horizontal
  style(legendgroup = NULL)

p2

saveWidget(p2, file = here("figs", "points_share_esc.html"))             # Save the plot as a html

```

### Visualisation 2 summary
Visualisation 2 is more successful at demonstrating the impact of the voting system changes have had on the points received by the winning songs than visualisation 1. 

In particular, visualisation 2 is effective at showing the impact that the voting system had on points allocation for the early years of the competition (1957-1974). The frequent changes in the voting system in the first 20 years of the competition led to large variability in the share of points achieved by the winning song. In 1964, Italy received the highest share of points in the Eurovision Song Contest so far with 34.03%. In contrast, Luxembourg received the lowest shared of points of any winning song in the contest in 1972 with 8.3%. The reason for this is that the voting system in 1972 meant that each country awarded more points to their favourite song and awarded more countries points, in comparison with the 1964 voting system.

Visualisation 2 also shows that the share of points has remained consistent between 1975 and 2022 because a similar voting system has been used since 1975. It is interesting that the share of points awarded to the winning song did not change from 2016, when the number of points awarded by each country was doubled. It would be interesting to see whether this continues for future competitions.


### Future Direction
There was some additional information about the voting system that was not added to this plot. Different years of the Eurovision Song Contest have used a Jury voting system, a televote/public voting system or a mixture of the two. It was decided that this information would not be important for this visualisation. However, it would be interesting if a future project visualised differences in the points allocation for these different types of voting systems.

Another interesting way to investigate the Eurovision data would be to visualise the effect of running order position on the points totals of each song in the contest. There is an assumption among Eurovision fans that the 2nd position is the worst position to perform from in either the semi-finals or the grand-final. It would be interesting to investigate whether this is true using a data visualisation.

Finally, this Eurovision data could also be used to determine whether certain countries are more likely to give points to one another. Many people view the points allocation process in Eurovision to be politically motivated, where certain countries are more likely to award points to one another. There may be some truth in this, given that Cyprus and Greece are notorious for giving one another maximum points each year. It would be interesting to find a way to visualise this in the future.

### References 
Repo: https://github.com/paulgering/PSY6422_project
Eurovision website: https://eurovision.tv
Eurovision.World website: https://eurovisionworld.com


